\documentclass[10pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[russian]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}


% меняем поля
\usepackage{geometry}
\geometry{left=3cm}
\geometry{right=2cm}
\geometry{top=2cm}
\geometry{bottom=2cm}

\begin{document}

\begin{center} 

\large SAINT-PETERSBURG STATE POLYTECHNICAL UNIVERSITY

\large Department of Computer Systems and Software engineering \\[8.5cm] 

\huge ESSAY \\[0.6cm] % название работы, затем отступ 0,6см
\large for first lecture\\
\large Discipline: <<Information security>>\\[4.5cm]

\end{center} 

\begin{flushright}
Performed: student gr. 53501/2 \\
Ponomarev M.A \\[1.0cm]


Teacher \\
Vilegzanina K.D
\end{flushright}


\vfill 

\begin{center} 
\large Saint-Petersburg \\
2015
\end{center} 

\thispagestyle{empty}

\newpage


\begin{center}
\huge \textbf{Essay about Human-Centered Study of a Network Operations Center
}
\end{center}
\bigskip

The first lecture was about network operations center (NOC) is the nerve center of of any large netwok's defense which has two main targets:

\begin{itemize}
	\item \textbf{Network defense analysts.} Responsibility for identifying, analyzing and reporting events that occured in the network.
	\item \textbf{Newtwork defense managers.} Responsibility for general situation awareness of the network.
\end{itemize}

The NOC is considered a sensitive information environment and access is restricted to those who worked on the operations floor. Nevertheless, the doors of this environmet are open for interviewers who can develop their understanding of what the NOC is. On the average, they are given 12 months to do that.

The strong point of NOC is its highly collaborative work environment. While each analyst has his own responsibilities, work in the NOC is a team effort.Analysts interact with other NOC analysts and people outside the NOC on a regular basis. The preferred method for sharing information was through verbal and physically co-located interactions.

To sum up, I find network operations center really perspictive and necessary which can help make our informational live safer. In spite of that, we have to be aware that the more we know about technologies of network defense the more secured is our PC.

\end{document}